\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-07-02 paper/subdocuments/results.Rnw
cleaned results.Rnw Comparison of FTA and HBS (unmarried)

\subsubsection{Normal versus special cases}

@@

##
# Unmarried ESTV
estv2010 <- read.csv("../../data/estv_normal_sonder_mitNuller_stE_2010.csv",sep=";")
estv2010.unmarried<-estv2010[c(18:38),c(1,3)]
names(estv2010.unmarried)[2]=c("unmarried")
##
# Simulate individual data points
# Percentile-Plot (descriptive  purpose)
# cumulative probabilites
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
# probabilities
prob<-c(cum.p[1],diff(cum.p), 1-0.9999)
# extreme values beyond x (to sample)
#freq<-max(normal$anz_pflichtige)
freq<-3000
init<-0
fin<-(abs(max(estv2010.unmarried$unmarried,na.rm=TRUE))+5)
# generate the sequence to take pairs from
ival<-c(init,estv2010.unmarried$unmarried,fin)
len<-10000 # sequence of each pair
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
estv2010.unmarried.ind<-data.frame(s)
names(estv2010.unmarried.ind)[1]=c("inc")
estv2010.unmarried.ind$inc<-estv2010.unmarried.ind$inc/1000

@@

density1 <- density(habe10.unmarried$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(min(rbind(density1$x,density2$x)), 800),
     ylim=c(0,max(rbind(density1$y,density2$y))))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(median(rbind(density1$x,density2$x)),median(rbind(density1$x,density2$x))),y=c(max(rbind(density1$y,density2$y)),max(rbind(density1$y,density2$y))))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(bd.2010.ind)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

par(mfrow=c(1,3))
g10 <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of HBS Distribution")
title(main=paste("Overall realtive density"))
abline(h=1,lty=2)
g1A <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=bd.2010.ind, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,2.5), ylab="",
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

>>>>

\emph{Normal versus special cases}

@@

@@

par(mfrow=c(1,2))
density1 <- density(habe10.unmarried$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(min(rbind(density1$x,density2$x)), 800),
     ylim=c(0,max(rbind(density1$y,density2$y))))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(median(rbind(density1$x,density2$x)),median(rbind(density1$x,density2$x))),y=c(max(rbind(density1$y,density2$y)),max(rbind(density1$y,density2$y))))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(bd.2010.ind)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

# Relative Distribution
# Overall and Median effect
#####
#g10 <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
 #              smooth=0.4, ci=FALSE,
#               yolabs=seq(-1,3,by=0.5),
   #            ylim=c(0.5,5.0),
    #           bar=TRUE, quiet=FALSE,
     #          xlab="Proportion of HBS Distribution")
#title(main=paste("Overall realtive density"))
#abline(h=1,lty=2)
#g1A <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
 #              show="effect",
  #             bar=TRUE, quiet=FALSE,
  #             ylim=c(0.5,5.0), ylab="",
  #             smooth=0.4, ci=FALSE,
  #             yolabs=seq(-1,3,by=0.5),
  #             xlab="Proportion of HBS Distribution")
#title(main=paste("Effect of Median shift"))
#abline(h=1,lty=2)

gA0 <- reldist(y=bd.2010.ind, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,2.5), ylab="",
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@
